The Galactic Midplane is Not a Plane: Implications for dynamical analysis with {\em Gaia} data and beyond

### 2019-04-22 paper/ms.tex
Change from cartoon to cartoon approximation

\subsection{Cartoon effect of midplane error} \label{ssec:cartoon}
We present a cartoon in Figure~\ref{fig:cartoon} to show how an inaccurate
determination of the midplane leads to a phase-dependence of the actions
calculated from an orbit specified by a phase-space point and an assumed
potential model. The $y$-axis corresponds to the vertical height of the orbit
and the $x$-axis orbital phase. The solid gray line indicates the ``true''
orbit of the star; that is, its orbit as it oscillates around the true
midplane. The dashed gray line is an erroneous midplane assigned to the
potential model which an observer uses to integrate the orbit of the star and
hence estimate its actions. The model potential is otherwise identical to the
one in which the star is actually moving.

@@

\begin{figure*}
\plotone{fig/cartoon.pdf}
\caption{Cartoon showing the effect an error in the determination of the
coordinate midplane can have on orbit integration and action estimation. The
$x$-axis shows the orbital phase and the $y$-axis the vertical height. The top
gray curve depicts an example ``true'' orbit oscillating about the true
midplane (horizontal solid gray line). Consider an observer who erroneously
assumes the midplane is located at the horizontal dashed line. Suppose this
observer measures the phase-space position of the star at two different
orbital phases (blue and pink points). If the observer were then to integrate
the star's orbit using a model potential with the erroneous midplane, they
would obtain the blue and pink curves for the star's orbit, respectively. The
actions estimated from these two  erroneous orbits would subsequently differ,
both from each other and from the actions estimated for the true orbit (in the
potential with the correct midplane). Hence an incorrect midplane in the
potential model assumed will induce phase-dependence in the actions estimated
for a given star in that potential.}
\label{fig:cartoon}
\end{figure*}

>>>>

\subsection{Cartoon effect of midplane error} \label{ssec:cartoon}
We present a cartoon approximation in Figure~\ref{fig:cartoon} to show how an inaccurate
determination of the midplane leads to a phase-dependence of the actions
calculated from an orbit specified by a phase-space point and an assumed
potential model. The $y$-axis corresponds to the vertical height of the orbit
and the $x$-axis orbital phase. The solid gray line indicates the ``true''
orbit of the star; that is, its orbit as it oscillates around the true
midplane. The dashed gray line is an erroneous midplane assigned to the
potential model which an observer uses to integrate the orbit of the star and
hence estimate its actions. The model potential is otherwise identical to the
one in which the star is actually moving.

@@

\begin{figure*}
\plotone{fig/cartoon.pdf}
\caption{Cartoon approximation showing the effect an error in the determination of the
coordinate midplane can have on orbit integration and action estimation. The
$x$-axis shows the orbital phase and the $y$-axis the vertical height. The top
gray curve depicts an example ``true'' orbit oscillating about the true
midplane (horizontal solid gray line). Consider an observer who erroneously
assumes the midplane is located at the horizontal dashed line. Suppose this
observer measures the phase-space position of the star at two different
orbital phases (blue and pink points). If the observer were then to integrate
the star's orbit using a model potential with the erroneous midplane, they
would obtain the blue and pink curves for the star's orbit, respectively. The
actions estimated from these two  erroneous orbits would subsequently differ,
both from each other and from the actions estimated for the true orbit (in the
potential with the correct midplane). Hence an incorrect midplane in the
potential model assumed will induce phase-dependence in the actions estimated
for a given star in that potential.}
\label{fig:cartoon}
\end{figure*}
